Ecuador plant species GBIF cleaning

### 2022-10-31 code/L1/L1_Ecuador_plants_GBIF.Rmd
formatting changes and removing unnecessary duplicate code

---
title: "Ecuador plant species GBIF cleaning"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "TBD"
data output: "TBD"
project: "Frugivoria"
date: "2022-10-12"
output: html_document
---

@@

```{r}
# Collection codes, people names, collector number and dates
occs <- formatOcc(occs)
# Locality information
occs <- formatLoc(occs)
# Geographical coordinates
occs <- formatCoord(occs)
# Species and family names
occs <- formatTax(occs)
```

@@

```{r}
# Duplicate specimens
dups <- prepDup(occs, 
                comb.fields =   list(c("family","col.last.name","col.number","col.loc"),
     c("family","col.last.name","col.number","col.year")))
dups <- getDup(dups)
head(dups[order(dups$dup.ID),],6)
table(dups$dup.prop)
occs <- cbind.data.frame(occs, 
                         dups[,c("dup.ID", "dup.numb", "dup.prop")],
                         stringsAsFactors = FALSE)
occs <- mergeDup(occs)
table(occs$tax.check, occs$tax.check1)
table(occs$geo.check, occs$geo.check1)
table(occs$loc.check, occs$loc.check1)
occs <- validateDup(occs)
```

@@

```{r}
saveData(occs, by = "family")
Ecuador_GBIF_path <- file.path(output_path,"Ecuador_GBIF_occurences_plantR.csv") 
write.csv(d, file = Ecuador_GBIF_path)
```

>>>>

---
title: "Ecuador plant species GBIF cleaning"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "Ecuador_GBIF_occurences.csv"
data output: "TBD"
project: "Frugivoria"
date: "2022-10-12"
output: html_document
---

@@

```{r}
# Collection codes, people names, collector number and dates
occs <- formatOcc(occs)
```

```{r}
# Locality information
occs <- formatLoc(occs)
```

```{r}
# Geographical coordinates
occs <- formatCoord(occs)
```

```{r}
# Species and family names
occs <- formatTax(occs)
```

@@

```{r}
# Duplicate specimens
occs <- validateDup(occs)
```

@@

```{r}
saveData(occs, by = "geo", path = file.path(output_path, "Ecuador_GBIF_occurences_plantR_bygeo.csv"))
saveData(occs, by = "tax", path = file.path(output_path, "Ecuador_GBIF_occurences_plantR_bytax.csv"))
Ecuador_GBIF_path <- file.path(output_path,"Ecuador_GBIF_occurences_plantR.csv") 
write.csv(d, file = Ecuador_GBIF_path)
```
